---
title: "MLH04"
author: "Liu Zhe"
date: "2022-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = TRUE,
  warning = FALSE
)
```

## Environment Variables and Packages

```{r}
options(java.parameters = "-Xmx2048m",
        stringsAsFactors = FALSE, 
        encoding = 'UTF-8')

suppressPackageStartupMessages({
  # ISLR2
  library(ISLR2)
  # RG
  library(glmnet)
  # DM
  library(zip)
  library(openxlsx)
  library(readxl)
  library(writexl)
  library(RcppRoll)
  library(plyr)
  library(stringi)
  library(feather)
  library(RODBC)
  library(MASS)
  library(car)
  library(data.table)
  library(lubridate)
  library(plotly)
  library(pROC)
  library(tidymodels)
  library(tidyverse)
})
```

## College

Format College dataset: 

```{r}
college.format <- College %>% 
  mutate(Private = if_else(Private == 'Yes', 1, 0))
```

Split data into training and test set: 

```{r}
set.seed(1107)
college.test <- dplyr::sample_frac(college.format, 0.25)
college.train <- college.format[which(!(rownames(college.format) %in% rownames(college.test))), ]
```

Select explanatory variables by Stepwise regression: 

```{r}
college.inter <- lm(Apps ~ 1, data = college.train)
college.all <- lm(Apps ~ ., data = college.train)
college.both <- stats::step(college.inter, scope = formula(college.all), direction = 'both', trace = 0)
summary(college.both)
```

Select Accept, Top10perc, Expend, Outstate, Enroll. 

LR model: 

```{r}
college.lr <- lm(Apps ~ Accept + Top10perc + Expend + Outstate + Enroll, data = college.train)
summary(college.lr)
```

Test error of LR model: 

```{r}
college.test.lr <- college.test %>% 
  mutate(Apps_pred = predict(college.lr, newdata = college.test))

(with(college.test.lr, mse.lr <- mean(Apps - Apps_pred) ^ 2))
```

Best lambda for ridge regression model: 

```{r}
college.ridge.cv <- cv.glmnet(x = as.matrix(select(college.train, -Apps)), 
                              y = college.train$Apps, 
                              alpha = 0)

(college.ridge.lambda <- college.ridge.cv$lambda.min)
```

Ridge regression model: 

```{r}
college.ridge <- glmnet(x = as.matrix(select(college.train, -Apps)), 
                        y = college.train$Apps, 
                        alpha = 0, lambda = college.ridge.lambda)
coef(college.ridge)
```

Test error of ridge regression model: 

```{r}
college.test.ridge <- college.test %>% 
  mutate(Apps_pred = predict(college.ridge, newx = as.matrix(select(college.test, -Apps))))

(with(college.test.ridge, mse.ridge <- mean(Apps - Apps_pred) ^ 2))
```

Best lambda for LASSO regression: 

```{r}
college.lasso.cv <- cv.glmnet(x = as.matrix(select(college.train, -Apps)), 
                              y = college.train$Apps, 
                              alpha = 1)

(college.lasso.lambda <- college.lasso.cv$lambda.min)
```

LASSO regression model: 

```{r}
college.lasso <- glmnet(x = as.matrix(select(college.train, -Apps)), 
                        y = college.train$Apps, 
                        alpha = 1, lambda = college.lasso.lambda)
coef(college.lasso)
```

Test error of LASSO regression: 

```{r}
college.test.lasso <- college.test %>% 
  mutate(Apps_pred = predict(college.lasso, newx = as.matrix(select(college.test, -Apps))))

(with(college.test.lasso, mse.lasso <- mean(Apps - Apps_pred) ^ 2))
```

